Neural Circuit Discovery

### 2013-11-03 docs/paper/paper.tex
updates to plot

\section{Introduction}
``type'' is a recurreing theme in biology
Cell type in bio literature, stem cells, something something

It is only through understanding the types of the system that we can understand
its function.

\section{Methods}
Stochastic blockmodels long known

We take an infinite extension of the SBM (the IRM ) \todo{cite both}
and modify it to learn the structure of the underlying code.

Spatial component by performing a GLM-style link function.

Describe the model

We develop a series of Markov-chain monte carlo scheems to solve for
the posterior, presenting the MAP estimate. To avoid local minima we
slowly anneal, over 1000 iterations \todo{Fix numbers}.

Hyperparameter inference.

We show that we recover ground truth.

@@

\subsubsection{Mouse Retina}
The recent release of connectome-scale data for the mouse retina.

Look we recover known classes!

\subsection{Drosophila}

\subsection{C. elegans}

>>>>

\section{Introduction}
Computing systems, biological or human-engineered, contain computing
elements that can be classified into ``type'', which give
insight into function.

The rise of connectomics data allows discovery of cell types
based on connectivity information.

Here we describe a Bayesian non-parametric model that can discover
both the cell types and their patterns of interconnection automatically
from connectomics data.

We apply it to the recently-released mouse retina connectome, the
c. elegans connectome, and a ``connectome'' obtained by
reverse-engineering a portion of a classical microprocessor.

\section{Methods}
Stochastic block models assume a hidden or ``latent'' type is associated
wtih each node that ultimately influences its connectivity.

We extend this class of model to incorporate notions of spatial locality, 
as the connectivity of many neural systems is substantially constrained.

We perform posterior inference in this model using a series of Markov-chain
Monte Carlo techniques.

@@

\subsection{Synthetic Data}
We show our model works by generating synthetic data with known spatial/connectivity patterns and recovering ground truth, even when the generating process makes assumptions very different from our model.

\subsubsection{Mouse Retina}
When applied to the mouse retina dataset, we recover spatially-homogeneous patterns of activity that reflect a coarsening of ground truth.

\subsection{C. elegans}
When applied to c. elegans, we segregate ``head and sensor'' interneurons from the spatially-distributed neurons along the body axis.

\subsection{Microprocessor}

We recover the logical structure of the three primary registers of the
MOS6502 integrated circuit.
